### 2014-11-13 tex/intro.tex
boo

This summary heap algorithm defines how the bipartite graph is updated
during lazy initialization. Unlike GSE, however, the summary heap
algorithm introduces non-determinism in the search only at points of
divergence in the control flow graph. These points of non-determinism
are at field accesses or writes that lead to null-pointer exceptions
and at comparisons of references. The former represents a divergence
due to exceptional control flow while the latter is due to program
structure. The precise heap representation based on a bipartiate graph
coupled with this algorithm to perform updates to the heap enable us
to successfully mitigate the state space explosion problem in GSE.

@@

Aside from the novelty of the heap summary and its application to
symbolic execution, the new data structure appears to ameliorate state
explosion in symbolic execution as hoped. A preliminary implementation in Java
Pathfinder (JPF), described in this paper, compares the heap summary
algorithm on a handful of benchmarks, each representing different
degrees of initialization and branching, to GSE with lazy
initialization in Symbolic Pathfinder (SPF) and implementation
lazier\# also in SPF. The results show that in general, that the heap
summary algorithm improves over other techniques, and in some
instances, the improvement is remarkable: two-orders of magnitude
reduction in running time. More critically though, the heap summary
enables the initialization of larger more complex heaps than
heretofore possible as shown in our results.

@@

\item\textbf{-} A summary heap as a bipartite graph that supports aliasing, local value set computation, and heap updates.

@@

\end{compactdesc}
The rest of this paper defines summary heap and its to symbolic
execution. Following the algorithm definition, the existence proof of
bisimulation is given with the accompanying corollaries for soundness
and completeness. This is followed by the implementation in JPF and
the evaluation. The paper ends with the conclusion and future work.

>>>>

This summary heap algorithm defines how the bipartite graph is updated
during lazy initialization. Unlike GSE, however, the summary heap
algorithm introduces non-determinism in the search only at points of
divergence in the control flow graph. These points of non-determinism
are at field accesses or writes that lead to null-pointer exceptions
and at comparisons of references. The former represents a divergence
due to exceptional control flow while the latter is due to program
structure.

% The precise heap representation based on a bipartiate graph coupled
%with this algorithm to perform updates to the heap enable us to
%successfully mitigate the state space explosion problem in GSE.

@@

Aside from the novelty of the heap summary and its application to
symbolic execution, the new data structure appears to ameliorate state
explosion in symbolic execution as hoped. A preliminary implementation
in Java Pathfinder (JPF) shows that in general, that the heap summary
algorithm improves over other state-of-the-art techniques, and in some
instances, the improvement is remarkable: two-orders of magnitude
reduction in running time. More critically though, the heap summary
enables the initialization of larger more complex heaps than
heretofore possible as shown in our results.

%, described in this paper, compares the heap summary algorithm on a
%handful of benchmarks, each representing different degrees of
%initialization and branching, to GSE with lazy initialization in
%Symbolic Pathfinder (SPF) and implementation lazier\# also in
%SPF. The results

@@

\item\textbf{-} A summary heap as a bipartite graph that supports
  aliasing and does not require rewriting of constraints.

@@

\end{compactdesc}

%The rest of this paper defines summary heap and its to symbolic
%execution. Following the algorithm definition, the existence proof of
%bisimulation is given with the accompanying corollaries for soundness
%and completeness. This is followed by the implementation in JPF and
%the evaluation. The paper ends with the conclusion and future work.
